
\chapter{Summary}

\par MalbolgeLISP is an enormously big project. At 21'000 lines of pre-processed asm2bf code, 380'000 lines of low level assembly code and 368'000'000 bytes of Malbolge code, it's the largest project I ever worked on. I feel that I managed to accomplish my goal of creating the most complex Malbolge Unshackled program to date, while making it usable on contemporary mid-end PCs. I put months of research into Malbolge, and in total, I spent around two full months writing MalbolgeLISP, documenting it, optimising it, and polishing the Malbolge toolchain.

\par The Malbolge toolchain 57'000 lines of code, featuring C, C++, APL, Perl, Python, Lua, and many others. It's complexity grew over time, and in conjunction with asm2bf, I believe that it's the most complex project I have ever worked on. While developing and documenting it, I have:
\begin{itemize}
    \item improved my APL programming abilities.
    \item introduced myself to SAT solvers.
    \item stepped up my cryptography skills.
    \item learned how to implement functional languages in restricted environments.
    \item learned about many concepts in functional programming and mathematics that i didn't know about before.
    \item had an occasion to truly understand Lisp.
    \item improved at interpreter development.
    \item became better at point-free programming.
    \item managed to make one of my projects gain traction.
    \item done something new. Explored something that was yet unexplored. \textit{I was the best}.
\end{itemize}

\par Finally, I'd like to thank my girlfriend, Kiera, for giving me motivation to work and improve. She is someone i desperately needed in my life.
